Borel regularity for ODEs and Thimble Integrals

### 2024-02-08 exp-resurgence.tex
rewrite and cleaning

@@

\begin{abstract}
    ...
\end{abstract}
\tableofcontents

\begin{brainstorm}
    \item Section~\ref{borel_reg-ODE} and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
    \item Section~\ref{contour-argument-AL}---revise the general contour argument
    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
    \begin{itemize}
    \item Replace formalism in Section~\ref{sec:reg-decay}
    \end{itemize}
    \item Check which examples are still in the framework of our theorem
    \begin{itemize}
    \item Start a storage document for shelved examples
    \end{itemize}
    \item Section~\ref{resurgence-AL}---Draw intersection points figure
    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
    \item Explain contour figure in Airy example (explain what the regions indicate and what the color)
    \begin{itemize}
    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
    \end{itemize}
    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
    \begin{itemize}
    \item Put future goals in storage document
    \end{itemize}
    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
\end{brainstorm}

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

@@

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
\end{defn}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism. We'll denote such map with the symbol $\aexp$. More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e. as $z\to e^{i\theta}\infty$, we'll write $\aexp^\theta$.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. \textcolor{magenta}{The general example [not anymore---we've restricted]} is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

@@

\color{Goldenrod}
[These details are right above in Section~\ref{borel-reg:explanatory-power}!]
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
\color{black}
\begin{verify}
    Turn the ODE into a system: assume 
    \begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_\alpha^\theta \phi$ of a function on $\phi$ the position domain. In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$. Because this solution is so unique, its Laplace transform $\Phi_\alpha$ turns out to be Borel regular.

@@

\color{Goldenrod}
Then, our main result for thimble integrals is proving they are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
    Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}

@@

\[
{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\
& & &\\
\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]
\]

@@

 %  \textcolor{red}{Be careful with derivatives: maybe rewrite Lemma 3.8 in such a way that includes them. This means that equation 27 is not anymore algebraic, but it will include terms of the form $R_r(z) \tilde{W}^{(r)}$.
  % There is also another problem, the reasoning of Delabere in Lemma 3.9 requires the existence of a point $p_0$ in $\Omega'$ such that $|\hat{\psi}_j(p_0)|\leq |\hat{W}_m(p_0)|$ for every $m\geq 0$. Can we argue that $|\hat{\psi}_j(\rho e^{i\theta})|$ is bounded for $\rho\in [|\alpha_j|,|p|]$? }
%\end{proof}
\color{violet}
\subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
\textcolor{orange}{[Mention that this is a component of the earlier Borel regularity proof.]}
\color{black}
\subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}

>>>>

\usepackage{etoolbox}

\usetikzlibrary{math, 3d, calligraphy}

% --- styles ---

\definecolor{pwbeige}{RGB}{172, 146, 122}
\definecolor{pworange}{RGB}{245, 153, 30}

\tikzset{
  surf/.style={pwbeige!10},
  leaf/.style={thin, pwbeige!60},
  sing/.style={thick, pworange},
  ray/.style={thick}
}

% --- cotangent fibers ---

\newcommand{\rfiber}{1.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}

\newcommand{\drawfiber}{
  \foreach \sgn in {-1, 1} {
    \calligraphy[scale=\sgn, copperplate, heavy, heavy line width=0.25mm]
      (\rfiber, \rfiber) -- (\rfiber, -\rfiber)
      (\rfiber, -\rfiber) -- (-\rfiber, -\rfiber);
  };
}

% set up PGF keys
\pgfkeys{
  /laplace/.cd,
  drop/.store in=\fiberdrop,   drop/.value required,
  shade/.store in=\fibershade, shade/.default=true,
  degree/.store in=\fiberdeg,  degree/.value required,
  phase/.store in=\fiberphase, phase/.value required,
  dual/.store in=\fiberdual,   dual/.default=true
}

\newcommand{\fiberdescender}[1]{
  \calligraphy[copperplate, light, thin] (0, -\rfiber) -- (0, -#1);
}

\newcommand{\fibershading}[2]{
  \tikzmath{
    \shadestart = (-90 - #1) / \fiberdeg;
    \shadeend = (90 - #1) / \fiberdeg;
  }
  \fill[pwbeige!30, draw=pwbeige!60] (0, 0) -- (\shadestart:\rshade) arc (\shadestart:\shadeend:\rshade) -- cycle;
}

\newenvironment{fiber}[1][]{%
  \pgfkeys{/laplace/.cd, drop=0, shade=false, degree=1, phase=0, #1}
  \begin{scope}
    \fill[surf] (-\rfiber, -\rfiber) rectangle (\rfiber, \rfiber);
    \clip (-\rfiber, -\rfiber) rectangle (\rfiber, \rfiber);
    \tikzmath{
      if \fibershade then {
        print \fibershading{\fiberphase}{0};
      };
    }
}{% ...
  \end{scope}
  % see TikZ docs for branching statements
  % https://tikz.dev/library-math#sec-58.5
  \tikzmath{
    if \fiberdrop > 0 then {
      print \fiberdescender{\fiberdrop};
    };
  }
  \drawfiber
}

\newcommand{\genfibercontent}[1][]{
  \pgfkeys{/laplace/.cd, dual=false, #1}
  \pgfmathsetmacro{\hatch}{\rfiber/8};
  \pgfmathsetmacro{\firsthatch}{-\rfiber+\hatch}
  \pgfmathsetmacro{\nexthatch}{-\rfiber+2*\hatch}
  \pgfmathsetmacro{\hatchstop}{\rfiber-\hatch/2}
  \foreach \y in {\firsthatch, \nexthatch, ..., \hatchstop} {
    \tikzmath{
      coordinate \drawfrom;
      coordinate \drawto;
      if \fiberdual then {
        \drawfrom = (\y, -\rfiber);
        \drawto = (\y, \rfiber);
      } else {
        \drawfrom = (-\rfiber, \y);
        \drawto = (\rfiber, \y);
      };
    }
    \draw[leaf] (\drawfrom) -- (\drawto);
  };
  \fill circle (\dotsize);
}

\newcommand{\singfibercontent}{
  % nonsingular leaves
  \foreach \sector in {30, 90, ..., 330} {
    \tikzmath{
      \farout = 45*floor((\sector + 59) / 45);
      \tfarout = 3*(\farout - \sector);
      \rfarout = \rfiber/sin(45+mod(\farout-45, 90));
    }
    \pgfmathsetmacro{\rmax}{sin(\tfarout) * pow(\rfarout, 3)}
    \foreach \r in {0.5, 1.0, ..., \rmax} {
      \pgfmathsetmacro{\win}{asin(\r/(2*\rmax))}
      \draw[leaf, rotate=\sector, domain=\win:{180-\win}, variable=\t] plot ({\t/3}:{(\r/sin(\t))^(1/3)});
    };

    % singular leaves
    \foreach \ang in {90, 210, 330} {
      \draw[sing] (\ang:{-sqrt(2)*\rfiber}) -- (\ang:{sqrt(2)*\rfiber});
    };
    \fill[sing] circle (\dotsize);
  };
}

% --- posititon plane ---

\pgfmathsetmacro{\hatch}{2/3}
\tikzmath{
  \phase = 15;
  \dotsize = 0.04;
  \drop = 3.5;
  \xsing = 2;
  \zsing = 4*\hatch;
  \xgen = 6;
  \zgen = 8*\hatch;
  \rcut = 1/5;
}

\newcommand{\ray}[2]{
  \draw[ray] (#1, #2) -- (8, {#2 + (8-#1)*tan(\phase)});
}

% local picture of the Laplace transform
\newcommand{\basicLaplace}{
\begin{tikzpicture}[scale=0.9]
% position space
\begin{fiber}
  \genfibercontent
  \ray{0}{0}
\end{fiber}
\node[anchor=north, outer sep=1mm, font=\footnotesize]
  at (0, -\rfiber) {position space};

% frequency space
\begin{scope}[shift={(4 + 0.25*8/3, 0)}]
  \begin{fiber}[shade, phase=\phase]
    \genfibercontent[dual]
  \end{fiber}
  \node[anchor=north, outer sep=1mm, font=\footnotesize]
    at (0, -\rfiber) {frequency space};
\end{scope}
\end{tikzpicture}
} % \basicLaplace

% phase space picture of the Laplace transform
\newcommand{\phaseSpaceLaplace}{
\begin{tikzpicture}[z={(0.25cm, 0.2cm)}, scale=0.9]
% position plane
\begin{scope}[canvas is xz plane at y=0]
  % surface
  \fill[surf]
    (0, 0) -- (0, \zsing-\rcut)
    -- ++(\xsing-\rcut, 0) arc (-90:90:\rcut) -- (0, {\zsing + \rcut})
    -- (0, 8) --(8, 8) -- (8, 0) -- cycle;

  % hatching
  \pgfmathsetmacro{\nexthatch}{2*\hatch}
  \pgfmathsetmacro{\singstop}{\zsing - \hatch/2}
  \foreach \z in {\hatch, \nexthatch, ..., \singstop} {
    \draw[leaf] (0, \z) -- (8, \z);
  };
  \pgfmathsetmacro{\singstart}{\zsing + \hatch}
  \pgfmathsetmacro{\singnext}{\zsing + 2*\hatch}
  \pgfmathsetmacro{\hatchstop}{8 - \hatch/2}
  \foreach \z in {\singstart, \singnext, ..., \hatchstop} {
    \draw[leaf] (0, \z) -- (8, \z);
  };

  % singular leaves
  \begin{scope}[sing]
    \draw (\xsing, \zsing) -- (8, \zsing);
    \draw (0, \zsing-\rcut) -- ++(\xsing-\rcut, 0) arc (-90:90:\rcut) -- (0, {\zsing + \rcut});
  \end{scope}

  % integration rays
  \ray{\xgen}{\zgen}
  \ray{\xsing}{\zsing}

  % outline
  \calligraphy[copperplate, heavy, heavy line width=0.25mm]
    (0, 0) -- (0, \zsing-\rcut)
    (0, \zsing+\rcut) -- (0, 8)
    (0, 8) -- (8, 8)
    (8, 8) -- (8, 0)
    (8, 0) -- (0, 0);
\end{scope}

% generic fiber
\begin{scope}[canvas is xy plane at z=\zgen, shift={(\xgen, \drop)}]
  \begin{fiber}[drop=\drop, shade, phase=\phase]
    \genfibercontent[dual]
  \end{fiber}
\end{scope}

% singular fiber
\begin{scope}[canvas is xy plane at z=\zsing, shift={(\xsing, \drop)}]
  \begin{fiber}[drop=\drop, shade, degree=3, phase=\phase]
    \singfibercontent
  \end{fiber}
\end{scope}

% generic point
\fill (\xgen, 0, \zgen) circle (\dotsize);

% singular point
\fill[sing] (\xsing, 0, \zsing) circle (\dotsize);

% labels
\begin{scope}[overlay]
  \node (surf label) at (9, 0, 4) {$B$};
  \path (surf label) ++(0, \drop, 0) node {$T^*B$};
  \node[outer sep=0.15mm, font=\footnotesize, align=left]
    (cut label) at (-1.25, 1.2, \zsing) {branch cut \\ at conical \\ singularity};
  \draw[->] (cut label) to[out=-75, in=180] (-0.25, 0, \zsing);
\end{scope}
\end{tikzpicture}
} % \phaseSpaceLaplace

@@

\begin{abstract}
    Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics. Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles. In addition, we give a geometric description of the Borel plane.
\end{abstract}
\tableofcontents
%
%
%
\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

@@

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_{\zeta,b}^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_{\zeta,b}^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
\end{defn}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism. We'll denote such map with the symbol $\aexp$. More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e. as $z\to e^{i\theta}\infty$, we'll write $\aexp^\theta$.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. One example is Equation~\eqref{eqn:bessel-rescaled-1}, and we will cosndier equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

@@

\color{Goldenrod}
[These details are right above in Section~\ref{borel-reg:explanatory-power}!]
\begin{equation}%\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
\color{black}
\begin{verify}
    Turn the ODE into a system: assume 
    \begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function on $\phi$ the position domain. In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$. Because this solution is so unique, its Laplace transform $\Psi_\alpha$ turns out to be Borel regular.

@@

%\color{Goldenrod}
%Then, our main result for thimble integrals is proving they are indeed Borel regular:
%\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
 %   Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
%\begin{enumerate}
%\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
%\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
%\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
%\begin{multline}
%\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
%\end{multline}
%where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
%\end{enumerate}
%\end{theorem}

@@

%{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\
%& & &\\
%\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]

@@

 %  \textcolor{red}{Be careful with derivatives: maybe rewrite Lemma 3.8 in such a way that includes them. This means that equation 27 is not anymore algebraic, but it will include terms of the form $R_r(z) \tilde{W}^{(r)}$.
  % There is also another problem, the reasoning of Delabere in Lemma 3.9 requires the existence of a point $p_0$ in $\Omega'$ such that $|\hat{\psi}_j(p_0)|\leq |\hat{W}_m(p_0)|$ for every $m\geq 0$. Can we argue that $|\hat{\psi}_j(\rho e^{i\theta})|$ is bounded for $\rho\in [|\alpha_j|,|p|]$? }
%\end{proof}
\color{black}
\subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
